Population Inference of Non-Spinning Eccentric Binary Black Holes

### 2023-06-09 paper/paper.tex
Updates from Overleaf

\includegraphics[width=0.45\textwidth]{paper/figures/pop3d0.05.png}
\includegraphics[width=0.45\textwidth]{paper/figures/pop3d0.1.png}
\caption{\label{fig:pop3d0.05_0.1} Synthetic Population of EBBHs. The left figure represents the population for $\sigma_\epsilon=0.05$ and right figure represetns the population for $\sigma_\epsilon=0.1$}

\includegraphics[width=0.45\textwidth]{paper/figures/pop3d0.15.png}
\includegraphics[width=0.45\textwidth]{paper/figures/pop3d0.2.png}
\caption{\label{fig:pop3d0.15_0.2} Synthetic Population of EBBHs. The left figure represents the population for $\sigma_\epsilon=0.15$ and right figure represents the population for $\sigma_\epsilon=0.2$}

@@

\includegraphics[width=0.45\textwidth]{paper/figures/pop0.05.png}
\includegraphics[width=0.45\textwidth]{paper/figures/pop0.1.png}
\caption{\label{fig:pop_0.05_0.1} The left figure shows the primary mass vs secondary mass of the EBBHs and NEBBHs with $\sigma_\epsilon =0.05$. The right figure shows the same plot but for $\sigma_\epsilon=0.1$}

@@

\includegraphics[width=0.45\textwidth]{paper/figures/pop0.15.png}
\includegraphics[width=0.45\textwidth]{paper/figures/pop0.2.png}
\caption{\label{fig:pop_0.15_0.2} The left figure shows the primary mass vs secondary mass of the EBBHs and NEBBHs with $\sigma_\epsilon =0.15$. The right figure shows the same plot but for $\sigma_\epsilon=0.2$}

\end{figure*}
We have the total $100$ events with a minimum and maximum primary mass of $17.73 M_\odot$ and $49.14 M_\odot$, respectively. Similarly, we have the secondary minimum and maximum masses $10.11 M_\odot$ and $46.68 M_\odot$ given in Fig \ref{fig:pop2d05}.

@@

\includegraphics[width=0.95\textwidth]{paper/figures/corner0.05.png}
\caption{\label{fig:pop3d05}\textbf{3D-Synthetic Population of EBBHs}}

@@

\includegraphics[width=0.95\textwidth]{paper/figures/corner0.05scl.png}
\caption{\label{fig:pop3d05}\textbf{3D-Synthetic Population of EBBHs}}

>>>>

\begin{figure}[H]

\includegraphics[width=0.45\textwidth]{paper/figures/pop3d0.2.png}
\caption{\label{fig:pop3d0.2} Synthetic Population of EBBHs. The left figure represents the population for $\sigma_\epsilon=0.05$ and right figure represetns the population for $\sigma_\epsilon=0.1$}

\end{figure}

@@

\includegraphics[width=0.45\textwidth]{paper/figures/pop0.05.png}
\includegraphics[width=0.45\textwidth]{paper/figures/pop0.2.png}
\caption{\label{fig:pop_0.05_0.2} The left figure shows the primary mass vs secondary mass of the EBBHs and NEBBHs with $\sigma_\epsilon =0.05$. The right figure shows the same plot but for $\sigma_\epsilon=0.2$}

@@

@@

\includegraphics[width=0.95\textwidth]{paper/figures/corfig_0.05.png}
\caption{\label{fig:pop3d05}\textbf{Corner Plots for EBBHs and BBHS with $\sigma_\epsilon=0.05$}}

@@

\includegraphics[width=0.95\textwidth]{paper/figures/corfig_0.2.png}
\caption{\label{fig:pop3d05}\textbf{Corner Plots for EBBHs and BBHs with $\sigma_\epsilon=0.2$}}
